MCC Informativeness - Pilot with Kids

### 2018-10-31 stats/kids_Ex3_pref.Rmd
updating kids experiment - sam trial types in both halfs of exp 3 pref

---
title: "MCC Informativeness Kids 2"
author: "Manuel Bohn"
output: html_document
---

@@

## importing data
files <- dir("~/Work/MCC/git-mcc/kids_info_data/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,45,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

d_raw <-raw_data %>%
  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
         experiment = "mcc_kids_inf_2")

unique(d$subid)

log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf")%>%
  select(subid,experimenter,keep_drop,sex,dob)

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

>>>>

---
title: "MCC Ex3 Preference Kids"
author: "Manuel Bohn"
output: html_document
---

@@

## importing data
files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,45,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

d_raw <-raw_data

d_raw

### 2018-10-31 stats/mcc_inf.kids.Rmd
updating kids experiment - sam trial types in both halfs of exp 3 pref

---
title: "MCC Informativeness Kids"
author: "Manuel Bohn"
date: "26 4 2018"
output: html_document
---

```{r setup, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)

## importing data

d <- read_csv(file="kids_inf.data.csv")%>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

d %>%
  group_by(age)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)

@@

# Plot overall

```{r plot across age, echo = F }
p3 <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, subid) %>%
  summarise(correct = mean(correct))

@@

Here it seems like there is absolutely nothing for the 3yo. No difference between conditions and no performance above chance. That's bad news, especially since we have good reasons to believe that they are able to do this by that age. So it's reasonable to ask what's wrong with our setup? the next graph might give an answer to that

```{r plot by age, echo= FALSE}
p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(control,age, subid) %>%
  summarise(correct = mean(correct))

ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~age)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot for object picked based on position on table

There was a small tendency in the adult data to pick the inner object in the control condition (55% of cases). This is understandable as the agent is closer to that object and after turning it is the one that is closer in the agent's visual field (see below).

![Setup as is.](../../../setup_inf.png)

For the 3yo, it seems like the tendency to pick the object closer to the agent is much stronger and is in fact driving their choice. The plot below shows the proportion of trials in which they picked the inner object. If position would not matter, this should be at chance in each condition.

This bias seems to be absent in 4yo, so my prediction would be that we will see the effect in the full sample, whereas in the 2yo it is more likely to go away.

```{r plot for pick, echo = F }

p5 <- d%>%
  mutate(pick_position = ifelse(targetOnTable == "inner" & correct == 1, "inner", 
                             ifelse(targetOnTable == "outer" & correct == 1, "outer",
                                    ifelse(targetOnTable == "inner" & correct == 0, "outer",
                                           ifelse(targetOnTable == "outer" & correct == 0, "inner",NA)))),
         age = factor(age),
         control = ifelse(control == "true", "control", "test"))%>%
  group_by(age,control)%>%
  summarise(pick_inner = sum(pick_position == "inner")/length(pick_position))

ggplot(p5, aes(x = control, y = pick_inner, fill = age))+
  geom_bar(stat="identity", color = "black")+
  ylim(-0.05,1.05)+
  facet_wrap(~age)+
  theme_few() +
  geom_hline(yintercept = 0.5, lty=2)+
  scale_colour_solarized()

>>>>

---
title: "MCC Informativeness Kids 2"
author: "Manuel Bohn"
output: html_document
---

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

## importing data
files <- dir("~/Work/MCC/git-mcc/kids_info_data/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,45,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

d_raw <-raw_data %>%
  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
         experiment = "mcc_kids_inf_2")

log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf")%>%
  select(subid,experimenter,keep_drop,sex,dob)

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

@@

d %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)

@@

# Plot filler by age

```{r plot by age, echo= FALSE}
pf1 <- d %>%
      filter(trial == "filler1" | trial == "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

pf2 <- pf1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pf1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = pf2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

```{r plot by age, echo= FALSE}

p1 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Performance by trial
```{r plot trials}
ms <- d %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(subage, trial, subid) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = subage)) +
  geom_line(aes(group= subage)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

## Plot with age as continuous variable

```{r plot by numerical age}
p5 <- d %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_smooth(method = "loess", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot overall test

```{r plot across age, echo = F }
p3 <- d %>%
  filter(trial != "filler1",
  trial != "filler2")%>%
  group_by(control, subid) %>%
  summarise(correct = mean(correct))

@@

### 2018-10-31 stats/mcc_inf_pilot_kids.Rmd
updating kids experiment - sam trial types in both halfs of exp 3 pref

d_trees_left_right <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2",
         subage != "Test")
```

@@

p <- d_trees_left_right %>%
  group_by( subage, control, subid) %>%
  summarise(correct = mean(correct))

>>>>

d_trees_left_right <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2",
         subage != "Test")

d_3 <- bind_rows(d_trees,d_trees_left_right,d_robots)
```

@@

p <- d_trees_left_right %>%
  group_by( subage, control, subid) %>%
  summarise(correct = mean(correct))%>%
  ungroup()%>%
  add_row(subage = "2", control = "no", correct = 0, subid = "none")

p1 <- p %>%
  group_by(subage, control)%>%
  multi_boot_standard(col = "correct")
